Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-06-13 2020/OPTIMA/optima_paper.tex
check all paper

\begin{document}
%
\title{Parallel global optimization algorithm with uniform convergence
for solving a set of constrained global optimization problems\thanks{This study was supported
by the Russian Science Foundation, project No.\,16-11-10150.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Vladislav Sovrasov\and
Konstantin Barkalov
}
%
\authorrunning{V. Sovrasov et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{sovrasov.vladislav@itmm.unn.ru},
\email{konstantin.barkalov@itmm.unn.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In the present work, an extension of global optimization algorithm for solving a set of problems
simultaneously onto a case of problems with non-convex constraints is considered. The property
of uniform convergence inherent to the algorithm allows distributing the computation resources
in the optimal way since the errors of numerical solutions decrease with approximately equal
rates in all problems in the course of the execution of the algorithm. The algorithm assigns a
priority to each problem and performs the computations of the objective functions in several
problems in parallel at every iteration. Upon stop of the method at arbitrary time moment,
solutions of similar quality would be obtained in all problems of the series being solved. A series
of several problems arises if the global optimization problem has a discrete parameter or, for
example, in solving a multicriteria optimization problem using criteria convolution. The
considered algorithm employs Peano-type space-filling curves for the reduction of the
multidimensional optimization problems to the one-dimensional ones.  The efficiency of the
implemented algorithm was tested using the sets of artificially generated global optimization
problems as well as in solving a series of problems obtained as a result of scalarization of a
multicriteria optimization  problem. Also, the numerical experiments confirmed the uniform
convergence of the proposed method.

@@

The feasible domain \(G\) can also be defined by the constraints that essentially complicate the problem.
The problem statement in this case will take the following form:
\begin{equation}
  \label{eq:constrained_problem}
  \varphi(y^*)=\min\{\varphi(y):y\in G=D \cap \{y: g_j(y)\leqslant 0, 1\leqslant j\leqslant m\}\}.
\end{equation}

@@

Further, let us consider solving a series of \(q\) problems of the kind
(\ref{eq:constrained_problem}):
\begin{equation}
  \label{eq:many_problems}
  \min\left\{\varphi_1(y), y\in G_1 \right\}, \min\left\{\varphi_2(y), y\in G_2\right\},...,
\min\left\{\varphi_q(y), y\in G_q\right\}.
\end{equation}

@@

\begin{displaymath}
  \begin{array}{lr}
    \psi (x^{*})=\min_{x\in [0,1]}\psi (x), \\
    \psi (x)={\begin{cases}g_{\nu }(x)/H_{\nu },&\nu <M\\(g_{M}(x)-g_{M}^{*})/H_{M},&\nu
=M\end{cases}}
  \end{array}
\end{displaymath}

Here \(M=\max_{}^{}\left\{\nu (x):x\in [0,1]\right\}\) and \(g_{M}^{*}=\min
_{}^{}\left\{g_{M}(x):x\in \cap _{i=0}^{M-1}Q_{i}\right\}\).
Because of the definition of the number \(M\), the problem of finding \(g_{M}^{*}\) always
has a solution. If \(M=m+1\), then \(g_{M}^{*}=\varphi(x^{*})\).
The arcs of the functions \(\psi (x)\) are the H\"{o}lder ones within the sets
\(\cap _{i=0}^{j}Q_{i},0\leq j\leq M-1\)
with the constant 1, and \(\psi (x)\) itself can have the breaks of the first kind at the boundaries
of these sets.
Despite the values of the H\"{o}lder constants \(H_k\) and the value \(g_{M}^{*}\) are not
known in advance, these ones can be estimated in the course of solving the problem.

A set of triples \(\{(x_k,\nu_k,z_k)\}, 1\leqslant k\leqslant n\) constitutes the search information
accumulated by the method upon executing \(n\) steps.

@@

Step 1. Renumber the points of the set \(X_k=\{x^1,\dotsc,x^k\}\cup\{0\}\cup\{1\}\), which
includes the boundary points of the interval \([0,1]\) as well as the points of preceding trials by
the lower indices in the order of increasing coordinate values i. e.
\begin{equation}
  \label{eq:points}
  0=x_0<x_1<\dotsc<x_{k+1}=1
\end{equation}
and juxtapose the values \(z_{i}=g_{\nu }(x_{i}),\nu =\nu (x_{i}),i={\overline {1,k}}\) to these
ones.

Step 2. For each integer number \(\nu ,1\leqslant \nu \leqslant m+1\) determine the corresponding
set \(I_{\nu }\) of the lower indices of the points, which the values of the functions \(g_{\nu
}(x)\) are computed in:
\begin{displaymath}
  I_{\nu }=\{i:\nu (x_{i})=\nu ,1\leqslant i\leqslant k\},1\leq \nu \leqslant m+1,
\end{displaymath}
determine the maximum value of the index \(M=\max\{\nu (x_{i}),1\leq i\leq k\}\).

Step 3. Compute current estimate for the unknown H\"{o}lder constant:
\begin{equation}
  \label{step2}
  \mu _{\nu }=\max\{\frac{|g_{\nu }(x_{i})-g_{\nu }(x_{j})|}{(x_{i}-
x_{j})^{\frac{1}{N}}}:i,j\in I_{\nu },i>j\}.
\end{equation}
If the set \(I_{\nu }\) contains less than two elements or if the value \(\mu _{\nu }\) appears to
be equal to zero, then accept \(\mu _{\nu }=1\).

Step 4. For all nonempty sets \(I_{\nu },\nu ={\overline {1,M}}\) compute the estimates
\begin{equation}
  \label{eq:step_4}
  z_{\nu }^{*}={\begin{cases}\min\{g_{\nu }(x_{i}):x_{i}\in I_{\nu }\}&\nu =M\\-\varepsilon
_{\nu }&\nu <M\end{cases}},
\end{equation}
where the vector with the non-negative coordinates \(\varepsilon _{R}=(\varepsilon
_{1},..,\varepsilon _{m})\) is called the vector of reserves.

Step 5. For each interval \((x_{i-1};x_{i}),1\leqslant i\leqslant k\) compute the characteristic
\begin{equation}
  \label{step3_1}
  R(i)={\begin{cases}\Delta _{i}+{\frac {(z_{i}-z_{i-1})^{2}}{(r_{\nu }\mu _{\nu
})^{2}\Delta _{i}}}-2{\frac {z_{i}+z_{i-1}-2z_{\nu }^{*}}{r_{\nu }\mu _{\nu }}}&\nu =\nu
(x_{i})=\nu (x_{i-1})\\2\Delta _{i}-4{\frac {z_{i-1}-z_{\nu }^{*}}{r_{\nu }\mu _{\nu
}}}&\nu =\nu (x_{i-1})>\nu (x_{i})\\2\Delta _{i}-4{\frac {z_{i}-z_{\nu }^{*}}{r_{\nu }\mu
_{\nu }}}&\nu =\nu (x_{i})>\nu (x_{i-1})\end{cases}}
\end{equation}
where \(\Delta_{i}=(x_{i}-x_{i-1})^{\frac{1}{N}}\).
The magnitudes \(r_{\nu }>1,\nu ={\overline {1,m}}\) are the parameters of the algorithm.
The products \(r_{\nu}\mu_{\nu}\) used in computing the characteristics as the estimates of the
unknown H\"{o}lder constants depend on these ones.

Step 6. Select the maximum characteristic:
\begin{equation}
\label{step4}
t=\argmax_{1\leqslant i \leqslant k+1}R(i)
\end{equation}

Step 7. Perform the next trial in the middle of the interval \((x_{t-1};x_{t})\) if the indices of its
end points are not the same: \(x^{k+1}={\frac {1}{2}}(x_{t}+x_{t-1})\).
Otherwise, perform the trial at the point
\begin{displaymath}
  x^{k+1}={\frac {1}{2}}(x_{t}+x_{t-1})-\operatorname {sgn}(z_{t}-z_{t-1}){\frac {|z_{t}-
z_{t-1}|^{n}}{2r_{\nu }\mu _{\nu }^{n}}},\nu =\nu (x_{t})=\nu (x_{t-1}),
\end{displaymath}
and then increment \(k\) by 1.

The algorithm stops if the condition \(\Delta_{t}\leqslant \varepsilon\) is satisfied where
\(\varepsilon>0\) is a predefined precision.
The value
\begin{equation}
\varphi_k^*=\min_{1\leqslant i \leqslant k}\varphi(x_i), x_k^*=\argmin_{1\leqslant i \leqslant
k}\varphi(x_i)
\end{equation}
is accepted as the estimate of the global optimal solution.

@@

The conditions of convergence of the described in Section \ref{sec:method} method in case of \(q=1\) are given in \cite{Strongin2000}.
\begin{theorem} (Sufficient convergence conditions)
  \label{th:single_conv}
  Assume that the following conditions are true:
  \begin{enumerate}
    \item The problem (\ref{eq:constrained_problem}) has a solution.
    \item Functions \(g_j(y)\leqslant 0, 1\leqslant j\leqslant m + 1\) are Lipschitzian on \(D\) with
respective constants \(L_i\) over the domain \(D\) (here \(g_{m+1}(y)=\varphi(y)\)).
    \item Beginning with some step (i. e. if \(k\) from (\ref{eq:points}) is sufficiently large),
    the values \(\mu_\nu\) from \ref{step2} satisfy the inequalities
    \begin{equation}
      r_\nu\mu_\nu > 2^{3-1/N}L_\nu \sqrt{N+3},\: 1\leqslant \nu \leqslant m + 1.
    \end{equation}
  \end{enumerate}
  Then any limit point \(y\) of the sequence \(\{y_k\} = \{y(x_k)\}\) generated
  by the index method while solving the problerm
  (\ref{eq:constrained_problem}) is admissible and satisfies the conditions
\begin{equation}
  \label{eq:conv_cond}
  \varphi(\overline{y})=\{ \varphi(y^k): g_i(y^k)\leqslant 0,1\leqslant j\leqslant m, k=1,2,\dots\}=\varphi(y^*),
\end{equation}
  where \(y^*\) from (\ref{eq:constrained_problem}).
\end{theorem}

\begin{remark}
  \label{rem:r1}
  From the relationship between the Holder and Lipschitz constants and from the condition (\ref{eq:conv_cond}) it follows
  that the parameters \(r_\nu\) from (\ref{step3_1}) should satisfy the condition
  \begin{equation}
    r_\nu > 2^{2 - 1/N}.
  \end{equation}
\end{remark}

\begin{theorem} (On convergence condiotions) Let the conditions of the Theorem \ref{th:single_conv}
  are satisfied for all of \(q\) problems from the set \ref{eq:many_problems} separately.
  Then solving all of the \(q\) problems by the algorithm from Section \ref{sec:method} will
  generate \(q\) infinite sequences, for the limit points of which the Theorem \ref{th:single_conv}
  will be also true.
\end{theorem}
\begin{proof}
  Let us consider two random problems from the set \ref{eq:many_problems}.
  \begin{equation}
      \begin{array}{lr}
        \min\{\varphi(y):y\in D_1,\: g_j^\varphi(y)\leqslant 0, 1\leqslant j\leqslant m_1\} \\
        \min\{\psi(y):y\in D_2,\: g_j^\psi(y)\leqslant 0, 1\leqslant j\leqslant m_2\}
      \end{array}
  \end{equation}
  Let us denote the characteristics (\ref{step3_1}) for the first problem as \(R_\varphi(i)\)
  and for the second problem as \(R_\psi(j)\). Considering that, we have:
  \begin{equation}
      \begin{array}{lr}
        R_\varphi(t_\varphi)=\max_{1\leqslant i\leqslant k}R_\varphi(i), \\
        R_\psi(t_\psi)=\max_{1\leqslant j\leqslant s}R_\psi(j),
      \end{array}
  \end{equation}
  where \(k\) corresponds to the number of trials in the first problem and \(s\)
  corresponds to the number of trials in the second one. The sequence of trials \(\{v^k\}\)
  corresponds to the first problem and the sequence of trials \(\{u^s\}\)
  corresponds to the second problem. The values \(z^k=g^\varphi_\nu(v_k),\nu =\nu (v_{k})\) correspond to the
  trial points \(\{v^k\}\) and the values \(w^s=g^\psi_\nu(u_s),\nu =\nu(u_{s})\) correspond to the
  trial points \(\{u^s\}\).

  When the considered two problems are solved simultaneously, the algorithm selects
  an interval for the next trial according to the condition:
  \begin{equation}
    R(t) = \max\{R_\varphi(i),R_\psi(j)\}
  \end{equation}

  Let the algorithm is solving tho problems and the iterations conunter is \(l = k + s, l=0,1,2,\dots\).
  Then, since for all of the problems Theorem \ref{th:single_conv} is true, at least one of the sequences
  \(\{v^k\}\) and \(\{u^s\}\) will be infinite (let it be \(\{v^k\}\)). If we prove that both the
  sequences are infinite, this would lead us to convergence in both the considered problems.

@@

  Let us consider the first case: from (\ref{step2})
  \begin{displaymath}
    \frac{|z_i-z_{i-1}|}{\Delta_i} \leqslant \mu_{\varphi,\nu}.
  \end{displaymath}
  Considering that, we can establish an upper bound:
  \begin{displaymath}
    \frac{(z_i-z_{i-1})^2}{r_\nu^2\mu_{\varphi,\nu}^2\Delta_i}=\frac{(z_i-z_{i-1})^2\Delta_i}{(r_\nu\mu_{\varphi,\nu}\Delta_i)^2}
    \leqslant \frac{\Delta_i}{r_\nu^2}.
  \end{displaymath}
  Therefore using the first branch form rule (\ref{step3_1}) we have inequality
  \begin{equation}
    \label{eq:th1}
    R_\varphi(i)\leqslant\Delta_i(1 + \frac{1}{r_\nu^2}) - \frac{2(z_i+z_{i-1}-2z^*_\nu)}{r_\nu\mu_{\varphi,\nu}}
  \end{equation}
  Because \(\overline{v}\) is the limit point of the sequence \(\{v^k\}\) and \(\varphi(y(\overline{v}))\leqslant z^*_{\nu}, \nu=m+1\) or
  \(z^*_\nu=0, \nu<m+1\) and \(z_{i-1},z_i\to 0\) at \(k\to\infty\):
  \begin{equation}
    \label{eq:th2}
    \Delta_i\to 0, z_i+z_{i-1} - 2 z_\nu^*\to 0.
  \end{equation}
  In the second case (when one of the other two branches rule (\ref{step3_1}) is applied) from we have
  \begin{displaymath}
    R_\varphi(i)=2\Delta_i + 4\frac{z^*_\nu-z_i}{r_\nu\mu_{\varphi,\nu}}
  \end{displaymath}
  If \(z^*_\nu \ne 0\) then \(z_i-z^*_\nu \geqslant 0\) and
  \begin{equation}
    \label{eq:th3}
    R_\varphi(i)=2\Delta_i - 4\frac{z_i-z^*_\nu}{r_\nu\mu_{\varphi,\nu}} \leqslant 2\Delta_i.
  \end{equation}
  Otherwise because of \(\overline{v}\) is feasible point \(z_i\to 0\) at \(k\to\infty\).

@@

Along with GCGen system, the examples of its application and constructing the set of problems
each consisting of an objective function and two constraints generated by \(F_{GR}\)
\cite{grishaginClass} generator or GKLS \cite{Gaviano2003} one Are distributed.
GKLS \cite{Gaviano2003} allows obtaining the functions of predefined dimensionality and
with predefined number of extrema.
In combination with GCGen, two sets of 100 problems each of the dimensionalities 2 and 3
were generated.
Each problem had two constraints.
Also, in order to demonstrate the properties of the method to be preserved at essentially
different properties of the problems, a mixed class consisting of 50 problems with two-
dimensional GKLS functions and 50 problems with \(F_{GR}\) ones was generated.
Examples of contour plots of the considered problems are presented in Fig. \ref{fig:isolines}.
The feasible area is highlighted by color.

@@

A test problem was considered to be solved if the optimization method executes the next trial
\(y^k\) in the \(\delta\)-proximity of the global minimum \(y^*\) i. e.
\(\left\|y^k-y^*\right\|\leqslant \delta = 0.01\left\|b-a\right\|\)
Where \(a\) and \(b\) are the left and right boundaries of the hypercube from (\ref{eq:task}).
If this relation is not fulfilled upon reaching the limit of number of iterations, the problem was
considered to be not solved.

When evaluating the quality of the method and its implementation, besides the speedup due to
the parallelization and the work time,
Was taken into account as well.
The mean maximum distance (in terms of \(l_{\inf}\)-norm) form the current estimate of the
optimum to its actual position computed on the set of problems (\ref{eq:many_problems}):
\(D_{avg}\) and \(D_{max}\).
The dynamics of these magnitudes in the course of the optimization shows how uniformly the
method distributes the resources among the problems.

@@

The results of solving the test problems by the sequential and parallel versions of the modified
IAGS for solving the sets of problems are presented in Table \ref{tab:speedup}.
For all two-dimensional classes of problems, the parameter \(r=4.7\).
In the case of the three-dimensional problems, \(r=4.7,\: \varepsilon_\nu=0.1\).
In all experiments, an additional computational load was introduced into the objective function
and constraints so that the time of a single call of a problem function was equal to
approximately 1 ms.

@@

In the course of present work, the support of the nonlinear constraints was implemented in the
algorithm solving a set of the global optimization problems.
Also, the essential conditions of convergence for the developed method were obtained.
The numerical experiments demonstrating the advantages of the considered approach over
solving the problems separately were carried out.
The efficiency of solving a set of problems together was demonstrated by the example of
solving a multicriteria problem with nonlinear constraints.

In the course of further work, it is planned to improve current implementation of the algorithm
by reducing the costs of supporting the search information for the set of problems and, this way,
improving the indices of speedup in time due to the parallelization.
Also, it is planned to implement a version of considered algorithm working in the distributed
memory according to the scheme described in \cite{BarkalovLebedev2017_2}.

>>>>

\begin{document}
%
\title{Parallel global optimization algorithm with uniform convergence
for solving a set of constrained global optimization problems\thanks{This study was supported
by the Russian Science Foundation, project No.\,16-11-10150.}}
%
\titlerunning{Parallel global optimization algorithm with uniform convergence}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Vladislav Sovrasov\and
Konstantin Barkalov
}
%
\authorrunning{V. Sovrasov et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{sovrasov.vladislav@itmm.unn.ru},
\email{konstantin.barkalov@itmm.unn.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In the present work, an extension of global optimization algorithm for solving a set of problems
simultaneously onto a case of problems with non-convex constraints is considered. The property
of uniform convergence inherent to the algorithm allows distributing the computation resources
in the optimal way since the errors of numerical solutions decrease with approximately equal
rates in all problems in the course of the execution of the algorithm. The algorithm assigns a
priority to each problem and performs the computations of the objective functions in several
problems in parallel at every iteration. Upon stop of the method at arbitrary time moment,
solutions of similar quality would be obtained in all problems of the series being solved. A series
of several problems arises if the global optimization problem has a discrete parameter or, for
example, in solving a multicriteria optimization problem using criteria convolution. The
considered algorithm employs Peano-type space-filling curves for the reduction of the
multidimensional optimization problems to the one-dimensional ones.  The efficiency of the
implemented algorithm was tested using the sets of artificially generated global optimization
problems as well as in solving a series of problems obtained as a result of scalarization of a
multicriteria optimization  problem. Also, the numerical experiments confirmed the uniform
convergence of the proposed method.

@@

The feasible domain can also be defined by the constraints that essentially complicate the problem.
The problem statement in this case will take the following form:
\begin{equation}
  \label{eq:constrained_problem}
  \varphi(y^*)=\min\{\varphi(y):y\in D \cap \{y: g_j(y)\leqslant 0, 1\leqslant j\leqslant m\}\}.
\end{equation}

@@

Further, let us consider solving a series of \(q\) problems of the kind
(\ref{eq:constrained_problem}):
\begin{equation}
  \label{eq:many_problems}
  \min\left\{\varphi_1(y), y\in D_1 \right\}, \min\left\{\varphi_2(y), y\in D_2\right\},...,
\min\left\{\varphi_q(y), y\in D_q\right\}.
\end{equation}

@@

\begin{displaymath}
  \begin{array}{lr}
    \psi (x^{*})=\min_{x\in [0,1]}\psi (x), \\
    \psi (x)={\begin{cases}g_{\nu }(x)/H_{\nu },&\nu <M,\\(g_{M}(x)-g_{M}^{*})/H_{M},&\nu
=M.\end{cases}}
  \end{array}
\end{displaymath}
Here \(M=\max_{}^{}\left\{\nu (x):x\in [0,1]\right\}\) and \(g_{M}^{*}=\min
_{}^{}\left\{g_{M}(x):x\in \cap _{i=0}^{M-1}Q_{i}\right\}\).
Because of the definition of the number \(M\), the problem of finding \(g_{M}^{*}\) always
has a solution. If \(M=m+1\), then \(g_{M}^{*}=\varphi(x^{*})\).
The function \(\psi (x)\) satisfies the H\"{o}lder condition within the sets
\(\cap _{i=0}^{j}Q_{i},0\leq j\leq M-1\)
with the constant 1, and \(\psi (x)\) can have jump discontinuities at the boundaries
of these sets.
Despite the values of the H\"{o}lder constants \(H_k\) and the value \(g_{M}^{*}\) are not
known in advance, these ones can be estimated in the course of solving the problem.
A set of triples \(\{(x_k,\nu_k,z_k)\}, 1\leqslant k\leqslant n\), constitutes the search information
accumulated by the method upon executing \(n\) steps.

@@

Step 1. Renumber the points of the set \(X_k=\{x^1,\dotsc,x^k\}\cup\{0\}\cup\{1\}\), which
includes the boundary points of the interval \([0,1]\) as well as the points of preceding trials by
the lower indices in the order of increasing coordinate values, i.e.
\begin{equation}
  \label{eq:points}
  0=x_0<x_1<\dotsc<x_{k+1}=1,
\end{equation}
and juxtapose the values \(z_{i}=g_{\nu }(x_{i}),\nu =\nu (x_{i}),i={\overline {1,k}}\) to these
ones.

Step 2. For each integer number \(\nu ,1\leqslant \nu \leqslant m+1\), determine the corresponding
set \(I_{\nu }\) of the lower indices of the points, which the values of the functions \(g_{\nu
}(x)\) are computed in:
\begin{displaymath}
  I_{\nu }=\{i:\nu (x_{i})=\nu ,1\leqslant i\leqslant k\},1\leq \nu \leqslant m+1,
\end{displaymath}
and determine the maximum value of the index \(M=\max\{\nu (x_{i}),1\leq i\leq k\}\).

Step 3. Compute current estimate for the unknown H\"{o}lder constant:
\begin{equation}
  \label{step2}
  \mu _{\nu }=\max \left\{ \frac{|g_{\nu }(x_{i})-g_{\nu }(x_{j})|}{(x_{i}-
x_{j})^{\frac{1}{N}}}:i,j\in I_{\nu },i>j \right\}.
\end{equation}
If the set \(I_{\nu }\) contains less than two elements or if the value \(\mu _{\nu }\) appears to
be equal to zero, then accept \(\mu _{\nu }=1\).

Step 4. For all nonempty sets \(I_{\nu },\nu ={\overline {1,M}}\) compute the estimates
\begin{equation}
  \label{eq:step_4}
  z_{\nu }^{*}={\begin{cases}\min\{g_{\nu }(x_{i}):x_{i}\in I_{\nu }\},&\nu =M,\\-\varepsilon
_{\nu },&\nu <M,\end{cases}}
\end{equation}
where the vector with the non-negative coordinates \(\varepsilon _{R}=(\varepsilon
_{1},..,\varepsilon _{m})\) is called the vector of reserves.

Step 5. For each interval \((x_{i-1},x_{i}),1\leqslant i\leqslant k\) compute the characteristic
\begin{equation}
  \label{step3_1}
  R(i)={\begin{cases}\Delta _{i}+{\frac {(z_{i}-z_{i-1})^{2}}{(r_{\nu }\mu _{\nu
})^{2}\Delta _{i}}}-2{\frac {z_{i}+z_{i-1}-2z_{\nu }^{*}}{r_{\nu }\mu _{\nu }}},&\nu =\nu
(x_{i})=\nu (x_{i-1}),\\2\Delta _{i}-4{\frac {z_{i-1}-z_{\nu }^{*}}{r_{\nu }\mu _{\nu
}}},&\nu =\nu (x_{i-1})>\nu (x_{i}),\\2\Delta _{i}-4{\frac {z_{i}-z_{\nu }^{*}}{r_{\nu }\mu
_{\nu }}},&\nu =\nu (x_{i})>\nu (x_{i-1}),\end{cases}}
\end{equation}
where \(\Delta_{i}=(x_{i}-x_{i-1})^{\frac{1}{N}}\).
The values \(r_{\nu }>1,\nu ={\overline {1,m}}\) are the parameters of the algorithm.
The products \(r_{\nu}\mu_{\nu}\) used in computing the characteristics as the estimates of the
unknown H\"{o}lder constants depend on these ones.

Step 6. Select the maximum characteristic:
\begin{equation}
\label{step4}
t=\arg \max_{1\leqslant i \leqslant k+1}R(i).
\end{equation}

Step 7. Perform the next trial in the middle of the interval \((x_{t-1},x_{t})\) if the indices of its
end points are not the same: \(x^{k+1}={\frac {1}{2}}(x_{t}+x_{t-1})\).
Otherwise, perform the trial at the point
\begin{displaymath}
  x^{k+1}={\frac {1}{2}}(x_{t}+x_{t-1})-\operatorname {sgn}(z_{t}-z_{t-1}){\frac {|z_{t}-
z_{t-1}|^{n}}{2r_{\nu }\mu _{\nu }^{n}}},\nu =\nu (x_{t})=\nu (x_{t-1}),
\end{displaymath}
and then increment \(k\) by 1.

The algorithm stops if the condition \(\Delta_{t}\leqslant \varepsilon\) is satisfied where
\(\varepsilon>0\) is a predefined precision.
The values
\begin{equation}
\varphi_k^*=\min_{1\leqslant i \leqslant k}\varphi(x_i), \; x_k^*=\arg \min_{1\leqslant i \leqslant
k}\varphi(x_i)
\end{equation}
are accepted as the estimates of the global solution.

@@

The conditions of convergence of the described in Section \ref{sec:method} method in case of \(q=1\) are given in \cite{Strongin2000}.
\begin{theorem} (Sufficient convergence conditions)
  \label{th:single_conv}
  Assume that the following conditions are true:
  \begin{enumerate}
    \item The problem (\ref{eq:constrained_problem}) has a solution.
    \item Functions \(g_j(y)\leqslant 0, 1\leqslant j\leqslant m + 1\), are Lipschitzian with
respective constants \(L_i\) over the domain \(D\) (here \(g_{m+1}(y)=\varphi(y)\)).
    \item Beginning with some step (i.e. if \(k\) from (\ref{eq:points}) is sufficiently large),
    the values \(\mu_\nu\) from (\ref{step2}) satisfy the inequalities
    \begin{equation}
      r_\nu\mu_\nu > 2^{3-1/N}L_\nu \sqrt{N+3},\: 1\leqslant \nu \leqslant m + 1.
    \end{equation}
  \end{enumerate}
  Then any limit point \(\overline{y}\) of the sequence \(\{y_k\} = \{y(x_k)\}\) generated
  by the index method while solving the problerm
  (\ref{eq:constrained_problem}) is admissible and satisfies the conditions
\begin{equation}
  \label{eq:conv_cond}
  \varphi(\overline{y})=\{ \varphi(y^k): g_i(y^k)\leqslant 0,1\leqslant j\leqslant m, k=1,2,\dots\}=\varphi(y^*),
\end{equation}
  where \(y^*\) from (\ref{eq:constrained_problem}).
\end{theorem}

\begin{remark}
  \label{rem:r1}
  From the relationship between the H\"{o}lder and Lipschitz constants and from the condition (\ref{eq:conv_cond}) it follows
  that the parameters \(r_\nu\) from (\ref{step3_1}) should satisfy the condition
  \begin{equation}
    r_\nu > 2^{2 - 1/N}.
  \end{equation}
\end{remark}

\begin{theorem} (On convergence conditions) Let the conditions of the Theorem \ref{th:single_conv}
  are satisfied for all of \(q\) problems from the set (\ref{eq:many_problems}) separately.
  Then solving all of the \(q\) problems by the algorithm from Section \ref{sec:method} will
  generate \(q\) infinite sequences, for the limit points of which the Theorem \ref{th:single_conv}
  will be also true.
\end{theorem}
\begin{proof}
  Let us consider two random problems from the set \ref{eq:many_problems}.
  \begin{equation}
      \begin{array}{lr}
        \min\{\varphi(y):y\in D_1,\: g_j^\varphi(y)\leqslant 0, 1\leqslant j\leqslant m_1\} \\
        \min\{\psi(y):y\in D_2,\: g_j^\psi(y)\leqslant 0, 1\leqslant j\leqslant m_2\}
      \end{array}
  \end{equation}
  Let us denote the characteristics (\ref{step3_1}) for the first problem as \(R_\varphi(i)\)
  and for the second problem as \(R_\psi(j)\). Considering that, we have:
  \begin{equation}
      \begin{array}{lr}
        R_\varphi(t_\varphi)=\max_{1\leqslant i\leqslant k}R_\varphi(i), \\
        R_\psi(t_\psi)=\max_{1\leqslant j\leqslant s}R_\psi(j),
      \end{array}
  \end{equation}
  where \(k\) corresponds to the number of trials in the first problem and \(s\)
  corresponds to the number of trials in the second one. The sequence of trials \(\{v^k\}\)
  corresponds to the first problem and the sequence of trials \(\{u^s\}\)
  corresponds to the second problem. The values \(z^k=g^\varphi_\nu(v_k),\nu =\nu (v_{k})\) correspond to the
  trial points \(\{v^k\}\) and the values \(w^s=g^\psi_\nu(u_s),\nu =\nu(u_{s})\) correspond to the
  trial points \(\{u^s\}\).

  When the considered two problems are solved simultaneously, the algorithm selects
  an interval for the next trial according to the condition:
  \begin{equation}
    R(t) = \max\{R_\varphi(i),R_\psi(j)\}.
  \end{equation}

  Let the algorithm is solving two problems and the iterations counter is \(l = k + s, l=0,1,2,\dots\).
  Then, since for all of the problems Theorem \ref{th:single_conv} is true, at least one of the sequences
  \(\{v^k\}\) and \(\{u^s\}\) will be infinite (let it be \(\{v^k\}\)). If we prove that both the
  sequences are infinite, this would lead us to convergence in both the considered problems.

@@

  Let us consider the first case: from (\ref{step2})
  \begin{displaymath}
    \frac{|z_i-z_{i-1}|}{\Delta_i} \leqslant \mu_{\varphi,\nu}.
  \end{displaymath}
  Considering that, we can establish an upper bound:
  \begin{displaymath}
    \frac{(z_i-z_{i-1})^2}{r_\nu^2\mu_{\varphi,\nu}^2\Delta_i}=\frac{(z_i-z_{i-1})^2\Delta_i}{(r_\nu\mu_{\varphi,\nu}\Delta_i)^2}
    \leqslant \frac{\Delta_i}{r_\nu^2}.
  \end{displaymath}
  Therefore using the first branch form rule (\ref{step3_1}) we have inequality
  \begin{equation}
    \label{eq:th1}
    R_\varphi(i)\leqslant\Delta_i(1 + \frac{1}{r_\nu^2}) - \frac{2(z_i+z_{i-1}-2z^*_\nu)}{r_\nu\mu_{\varphi,\nu}}.
  \end{equation}
  Because \(\overline{v}\) is the limit point of the sequence \(\{v^k\}\) and \(\varphi(y(\overline{v}))\leqslant z^*_{\nu}, \nu=m+1\) or
  \(z^*_\nu=0, \nu<m+1\) and \(z_{i-1},z_i\to 0\) at \(k\to\infty\):
  \begin{equation}
    \label{eq:th2}
    \Delta_i\to 0, z_i+z_{i-1} - 2 z_\nu^*\to 0.
  \end{equation}
  In the second case (when one of the other two branches rule (\ref{step3_1}) is applied) from we have
  \begin{displaymath}
    R_\varphi(i)=2\Delta_i + 4\frac{z^*_\nu-z_i}{r_\nu\mu_{\varphi,\nu}}
  \end{displaymath}
  If \(z^*_\nu \ne 0\) then \(z_i-z^*_\nu \geqslant 0\) and
  \begin{equation}
    \label{eq:th3}
    R_\varphi(i)=2\Delta_i - 4\frac{z_i-z^*_\nu}{r_\nu\mu_{\varphi,\nu}} \leqslant 2\Delta_i.
  \end{equation}
  Otherwise because of \(\overline{v}\) is feasible point \(z_i\to 0\) at \(k\to\infty\).

@@

Along with GCGen system, the examples of its application and constructing the set of problems
each consisting of an objective function and two constraints generated by \(F_{GR}\)
\cite{grishaginClass} generator or GKLS \cite{Gaviano2003} one Are distributed.
GKLS \cite{Gaviano2003} allows obtaining the functions of predefined dimensionality and
with predefined number of extrema.
In combination with GCGen, two sets of 100 problems each of the dimensionalities 2 and 3
were generated.
Each problem had two constraints.
Also, in order to demonstrate the properties of the method to be preserved at essentially
different properties of the problems, a mixed class consisting of 50 problems with 
two-dimensional GKLS functions and 50 problems with \(F_{GR}\) ones was generated.
Examples of contour plots of the considered problems are presented in Fig. \ref{fig:isolines}.
The feasible domain is highlighted by color.

@@

A test problem was considered to be solved if the optimization method executes the next trial
\(y^k\) in the \(\delta\)-vicinity of the global minimizer \(y^*\), i.e.
\(\left\|y^k-y^*\right\|\leqslant \delta = 0.01\left\|b-a\right\|\), 
where \(a\) and \(b\) are the left and right boundaries of the hypercube from (\ref{eq:task}).
If this relation is not fulfilled upon reaching the limit of number of iterations, the problem was
considered to be not solved.

When evaluating the quality of the method and its implementation, besides the speedup due to
the parallelization and the work time,
Was taken into account as well.
The mean maximum distance (in terms of \(l_{\infty}\)-norm) form the current estimate of the
optimum to its actual position computed on the set of problems (\ref{eq:many_problems}):
\(D_{avg}\) and \(D_{max}\).
The dynamics of these magnitudes in the course of the optimization shows how uniformly the
method distributes the resources among the problems.

@@

The results of solving the test problems by the sequential and parallel versions of the modified
IAGS for solving the sets of problems are presented in Table~\ref{tab:speedup}.
For all two-dimensional classes of problems, the parameter \(r=4.7\).
In the case of the three-dimensional problems, \(r=4.7,\: \varepsilon_\nu=0.1\).
In all experiments, an additional computational load was introduced into the objective function
and constraints so that the time of a single call of a problem function was equal to
approximately 1 ms.

@@

In the course of present work, the support of the non-convex constraints was implemented in the
algorithm solving a set of the global optimization problems.
Also, the sufficient conditions of convergence for the developed method were obtained.
The numerical experiments demonstrating the advantages of the considered approach over
solving the problems separately were carried out.
The efficiency of solving a set of problems together was demonstrated by the example of
solving a multicriteria problem with nonlinear constraints.

In the course of further work, it is planned to improve current implementation of the algorithm
by reducing the costs of supporting the search information for the set of problems and, this way,
improving the indices of time speedup due to the parallelization.
Also, it is planned to implement a version of considered algorithm working in the distributed
memory according to the scheme described in \cite{BarkalovLebedev2017_2}.
